Daily goals

### 2020-07-10 _TODO.Rmd
updating todos

@@

- [ ] determining the root
  - [ ] write something about the need to set the root to be able to do comparisons
  - [ ] say that utis hard to set it up automatically and that solutions are being sought

>>>>

- [ ] from phylotar paper: "requires stand-alone BLAST. Instructions for installing the BLAST+ suite can be found via NCBI [27]"

@@

- [x] determining the root
  - [ ] write something about the need to set the root to be able to do comparisons
  - [ ] say that it is hard to set it up automatically and that solutions are being sought
